Color- and piece-blind chess

### 2019-04-03 chess/papers/blind.tex
Some misc improvements while wrapping up NaN gate talk

Say \verb+blind_kings+ is playing as black; it remains easy to fool it
by moving black pieces into white's camp, since they are usually then
predicted to be white pieces. We can defend against this somewhat.
Since it is illegal to capture one's own piece, there is little risk
in trying; if it is indeed our own piece then the move will be
rejected, and if it is not our piece, then capturing is good for two
reasons: One, we capture a piece, and two, we avoid having
Stockfish make a move in this incorrectly predicted board. (Of course
there are many reasons why eagerly capturing a piece can be a bad
idea, but at this level of play, an edge in material is likely worth
it.)

@@

I would like to thank the little people (pawns) and the the author-
and content-blind anonymous referrees.

>>>>

Say \verb+blind_kings+ is playing as white; it remains easy to fool it
by moving black pieces into white's camp, since they are usually then
predicted to be white pieces. We can defend against this somewhat.
Since it is illegal to capture one's own piece, there is little risk
in trying; if it is indeed our own piece then the move will be
rejected, and if it is not our piece, then capturing is good for two
reasons: One, we capture a piece, and two, we avoid having
Stockfish make a move in this incorrectly predicted board. (Of course
there are many reasons why eagerly capturing a piece can be a bad
idea, but at this level of play, an edge in material is likely worth
it.)

@@

I would like to thank the little people (pawns) and the author-
and content-blind anonymous referrees.
